A hazards approach to the biometric analysis of infant mortality

### 2023-03-20 paper2.Rmd
work on birth cohorts

```{r plotcohort, fig.cap = "By birth month, cohorts.", fig.height = 9, eval = FALSE}
oldpar <- par(mfrow = c(4, 3))
for (mon in levels(dat$bmonth)){
    drawBB2(dat[dat$bmonth == mon, ], main = mon, printLegend = FALSE)
}
par(oldpar)
```

>>>>

```{r plotcohort, fig.cap = "By birth month, cohorts.", fig.height = 9, eval = TRUE}
oldpar <- par(mfrow = c(1, 1))
dato <- dat[dat$birthdate < as.Date("1950-12-31"), ]
fit <- coxreg(Surv(g(enter), g(exit), event) ~ strata(bmonth), data = dato)
cols <- c("blue", "magenta", rep("red", 4), rep("green", 3), "magenta", "blue", "blue")
haz <- hazards(fit)
pd <- numeric(12)
for(i in 1:12){
    haz[[i]] <- rbind(c(0, 0), haz[[i]])
    haz[[i]][, 2] <- cumsum(haz[[i]][, 2])
    pd[i] <- round((1 - exp(-max(haz[[i]][, 2]))) * 100, 1)
}
plot(haz[[1]][, 1], haz[[1]][, 2], col = cols[1], axes = FALSE, 
     type = "l", xlab = "Days", ylab = "Cumulative hazards")
for (i in 2:12){
    lines(haz[[i]][, 1], haz[[i]][, 2], col = cols[i], type = "l", lty = i)
}
legend("topleft", legend = paste(month.abb, pd, sep = ":  "), lty = 1:12, col = cols)
att <- c(0, 28, 183, 365)
axis(1, at = g(att), labels = att)
axis(2, las = 1)
box()
abline(v = g(28), lty = 3)
abline(h = 0)
fita <- coxreg(Surv(g(enter), g(exit), event) ~ 1, data = dato)
haza <- hazards(fita)
lines(c(0, haza[[1]][, 1]), cumsum(c(0, haza[[1]][, 2])), type = "l", lwd = 2, col = "black")
legend(100, 0.08, legend = "All", lty = 1, col = "black", lwd = 2)
par(oldpar)
```
